---
  title: "03 - Central Estimates"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{03 - Central Estimates}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
  
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Central estimate runs are carried out using the second query in the /src/ folder, 02_burden_central_estimate. They depend on the data generated using the 01_input_data_setup query. One run is carried out for each vaccination scenario, each corresponding to a set of input data in the /archive/01_input_data_setup folder. If the folder IDs were saved when input data was generated, the saved information can be used to identify the scenario data:

```{r,eval=FALSE}
library(YEP)
path=substr(getwd(),1,nchar(getwd())-10) #Path = repository folder
source(paste0(path,"/R/additional_functions.R"))
scenario_list=read.csv(file=paste0(path,"/shared/input_data_list.csv"),header=TRUE)
scenarios=scenario_list$scenario
input_data_ids=scenario_list$id
input_data_ids
```

```{r,eval=FALSE}
countries_to_run_file=paste0(path,"/shared/countries_select.csv")
central_estimate_ids=rep("",4)
for(n_run in 1:length(scenarios)){
  central_estimate_ids[n_run]=orderly2::orderly_run("02_burden_central_estimate",
  list(life_exp_file = "life_expectancy.csv", 
  countries_to_run_file = paste0(path, "/shared/countries_all.csv"), 
  input_id = input_data_ids[n_run], 
  YLD_per_case = 0.006486, 
  n_reps = 1,
  mode_parallel = TRUE, 
  n_cores=4),
  echo=FALSE)
}
write.csv(data.frame(scenario=scenarios,id=central_estimate_ids),file=paste0(path,"/shared/output_list1_central_estimates.csv"),row.names=FALSE)
```